A Test of the Frequency Independence Assumption of Power System Coefficients used in Geomagnetically Induced Current Estimates

### 2019-07-22 paper.tex
Updates from Overleaf

\section{Discussion}

@@

\acknowledgments
Magnetic and electric field measurements made at the Kakioka Magnetic Observatory was obtained from the Japan Meteorological Agency Data Portal \url{http://www.kakioka-jma.go.jp/obsdata/metadata/en}. The geomagnetic coordinates in Figure~\ref{map} were computed using code from \url{https://www.ngdc.noaa.gov/geomag/geom_util/apex.shtml}. We would like to thank the Hokkaido Electric Power Co. for the GIC measurements at the Memanbetsu substation and Shinichi Watari for communicating and preparing the GIC data and providing feedback on the manuscript. We also thank Ikuko Fujii for providing clarifications on the geoelectric instrument response, Trevor Gaunt and Emanuel Benabeau for review and comments on part (1) of Section 5, and Josh Rigler for substantial feedback and review.
%\clearpage

>>>>

\section{Discussion}
\label{discussion}

@@

\acknowledgments
Magnetic and electric field measurements made at the Kakioka Magnetic Observatory was obtained from the Japan Meteorological Agency Data Portal \url{http://www.kakioka-jma.go.jp/obsdata/metadata/en}. The geomagnetic coordinates in Figure~\ref{map} were computed using code from \url{https://www.ngdc.noaa.gov/geomag/geom_util/apex.shtml}. We would like to thank the Hokkaido Electric Power Co. for the GIC measurements at the Memanbetsu substation and Shinichi Watari for communicating and preparing the GIC data and providing feedback on the manuscript. We also thank Ikuko Fujii for providing clarifications on the geoelectric instrument response, Trevor Gaunt and Emanuel Benabeau for review and comments on part (1) of Section\ref{discussion}, and Josh Rigler for substantial feedback and review.
%\clearpage
